Emergent dual scaling of riverine biodiversity

### 2021-06-30 manuscript_pnas.Rmd
Update manuscript_pnas.Rmd

Third parties provided data for empirical data analysis; references are provided where appropriate. R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>). Codes for simulations, statistical analysis, figures, and tables are available at <https://github.com/aterui/public-proj_stream-diversity>.

>>>>

Part of our fish data set is available from the RiverFishTIME database [@comteRivFishTIMEGlobalDatabase2021]. The fish data provided by third parties are not available due to licensing issues. Environmental data are available at MERIT Hydro (http://hydro.iis.u-tokyo.ac.jp/\~yamadai/MERIT_Hydro/) [@yamazakiMERITHydroHighResolution2019], Global 3-second/1-second Water Body Map (http://hydro.iis.u-tokyo.ac.jp/\~yamadai/G3WBM/index.html) [@yamazakiDevelopmentGlobal90m2015],WorldClim (https://www.worldclim.org/data/v1.4/worldclim14.html) [@hijmansVeryHighResolution2005], Copernicus Global Land Service (https:/doi.org/10.5281/zenodo.3939038) [@marcelbuchhornCopernicusGlobalLand2020], and Global Reservoir and Dam database (https://doi.org/10.7927/H4N877QK) [@lehnerGlobalReservoirDam2011]. R functions for the generation of branching networks and the metacommunity simulation are provided as the R package 'mcbrnet' (available at <https://github.com/aterui/mcbrnet>). Codes for simulations, statistical analysis, figures, and tables are available at <https://github.com/aterui/public-proj_stream-diversity>.
